Quantifying Stability and Change in Personal Culture Using Panel Data

### 2023-10-02 manuscript/manuscript.Rmd
moved note

To compare these competing propositions, we calculate $\omega$ values separately for people with at least a bachelor's degree and people with less than a bachelor's degree at wave 1[^4] of the three General Social Survey's panels. We focus on the GSS because it contains the largest number of questions tapping general political dispositions, which is the domain where education has proven particularly relevant for understanding attitude stability. The GSS also covers a turbulent window of American politics from 2006 to 2014. This window covers the start of the Great Recession, debates about federal intervention in and regulation of Wall Street, the election of Barack Obama as the first black U.S. president, debates about the role of the federal government in the health care sector, the emergence of the Tea Party, and political realignment and clarification on the issue of gay marriage, among other topics.

>>>>

To compare these competing propositions, we calculate $\omega$ values separately for people with at least a bachelor's degree and people with less than a bachelor's degree at wave 1 of the three General Social Survey's panels.[^4] We focus on the GSS because it contains the largest number of questions tapping general political dispositions, which is the domain where education has proven particularly relevant for understanding attitude stability. The GSS also covers a turbulent window of American politics from 2006 to 2014. This window covers the start of the Great Recession, debates about federal intervention in and regulation of Wall Street, the election of Barack Obama as the first black U.S. president, debates about the role of the federal government in the health care sector, the emergence of the Tea Party, and political realignment and clarification on the issue of gay marriage, among other topics.

### 2023-10-02 manuscript/manuscript.tex
moved note

To compare these competing propositions, we calculate \(\omega\) values
separately for people with at least a bachelor's degree and people with
less than a bachelor's degree at wave 1\footnote{A small number of
  respondents report different highest degrees at wave 1, wave 2, and
  wave 3. Some of this is due to measurement error, and some of it is
  due to a small number of people obtaining a higher degree during the
  four years of the panel. Estimating the panel with highest at wave 1
  or highest degree reported across the panel produces functionally
  identical results.} of the three General Social Survey's panels. We
focus on the GSS because it contains the largest number of questions
tapping general political dispositions, which is the domain where
education has proven particularly relevant for understanding attitude
stability. The GSS also covers a turbulent window of American politics
from 2006 to 2014. This window covers the start of the Great Recession,
debates about federal intervention in and regulation of Wall Street, the
election of Barack Obama as the first black U.S. president, debates
about the role of the federal government in the health care sector, the
emergence of the Tea Party, and political realignment and clarification
on the issue of gay marriage, among other topics.

>>>>

To compare these competing propositions, we calculate \(\omega\) values
separately for people with at least a bachelor's degree and people with
less than a bachelor's degree at wave 1 of the three General Social
Survey's panels.\footnote{A small number of respondents report different
  highest degrees at wave 1, wave 2, and wave 3. Some of this is due to
  measurement error, and some of it is due to a small number of people
  obtaining a higher degree during the four years of the panel.
  Estimating the panel with highest at wave 1 or highest degree reported
  across the panel produces functionally identical results.} We focus on
the GSS because it contains the largest number of questions tapping
general political dispositions, which is the domain where education has
proven particularly relevant for understanding attitude stability. The
GSS also covers a turbulent window of American politics from 2006 to
2014. This window covers the start of the Great Recession, debates about
federal intervention in and regulation of Wall Street, the election of
Barack Obama as the first black U.S. president, debates about the role
of the federal government in the health care sector, the emergence of
the Tea Party, and political realignment and clarification on the issue
of gay marriage, among other topics.
